%% ============================================================
%%  References
%% ============================================================
\begin{thebibliography}{99}

\bibitem{ieee8021x} IEEE Standard for Local and Metropolitan Area Networks - Port-Based Network Access Control, \textit{IEEE Std 802.1X-2020}, IEEE, 2020.
\bibitem{rfc6614} S. Winter, M. McCauley, S. Venaas, and K. Wierenga, ``Transport Layer Security (TLS) Encryption for RADIUS,'' \textit{RFC 6614}, IETF, 2012.
\bibitem{rfc9190} J. P. Mattsson, M. Sethi, and D. Migault, ``EAP-TLS 1.3: Using the Extensible Authentication Protocol with TLS 1.3,'' \textit{RFC 9190}, IETF, 2022.
\bibitem{rfc7542} A. DeKok, ``The Network Access Identifier,'' \textit{RFC 7542}, IETF, 2015.
\bibitem{rfc7593} S. Winter, K. Wierenga, L. Lynch, and H. Zorn, ``The eduroam Architecture for Network Roaming,'' \textit{RFC 7593}, IETF, 2015.
\bibitem{rfc7348} M. Mahalingam \textit{et al.}, ``Virtual eXtensible Local Area Network (VXLAN),'' \textit{RFC 7348}, IETF, 2014.
\bibitem{passpoint2024} Wi-Fi Alliance, \textit{Passpoint: Seamless, Secure Wi-Fi Access}, Technical and Certification Documentation, 2024.
\bibitem{wba-openroaming} Wireless Broadband Alliance, \textit{OpenRoaming: Secure Global Wi-Fi Federation}, Industry Technical Documentation, 2024.
\bibitem{3gpp-ts23501} 3GPP, \textit{System Architecture for the 5G System (5GS)}, TS 23.501, Release 17, 2022.
\bibitem{etsi-mec002} ETSI, \textit{Multi-Access Edge Computing (MEC): Technical Requirements}, GS MEC 002, 2016.
\bibitem{hoiland2018xdp} T. Høiland-Jørgensen \textit{et al.}, ``The eXpress Data Path: Fast Programmable Packet Processing in the Operating System Kernel,'' in \textit{Proc. ACM CoNEXT}, 2018.
\bibitem{wireguard2017} J. A. Donenfeld, ``WireGuard: Next Generation Kernel Network Tunnel,'' in \textit{Proc. NDSS}, 2017.
\bibitem{openwrt2024} OpenWrt Project, \textit{OpenWrt Documentation}, Online Technical Documentation, 2024.
\bibitem{kipf2017gcn} T. N. Kipf and M. Welling, ``Semi-Supervised Classification with Graph Convolutional Networks,'' in \textit{Proc. ICLR}, 2017.
\bibitem{velickovic2018gat} P. Veličković \textit{et al.}, ``Graph Attention Networks,'' in \textit{Proc. ICLR}, 2018.
\bibitem{shen2021gnn} Y. Shen \textit{et al.}, ``Graph Neural Networks for Scalable Radio Resource Management: Architecture Design and Theoretical Analysis,'' \textit{IEEE J. Sel. Areas Commun.}, vol. 39, no. 1, pp. 101--115, 2021.
\bibitem{raissi2019pinn} M. Raissi, P. Perdikaris, and G. E. Karniadakis, ``Physics-Informed Neural Networks: A Deep Learning Framework for Solving Forward and Inverse Problems Involving Nonlinear PDEs,'' \textit{J. Comput. Phys.}, vol. 378, pp. 686--707, 2019.
\bibitem{schulman2017ppo} J. Schulman \textit{et al.}, ``Proximal Policy Optimization Algorithms,'' \textit{arXiv:1707.06347}, 2017.
\bibitem{altman1999cmdp} E. Altman, \textit{Constrained Markov Decision Processes}, Chapman and Hall/CRC, 1999.
\bibitem{jain1984} R. K. Jain, D.-M. W. Chiu, and W. R. Hawe, ``A Quantitative Measure of Fairness and Discrimination for Resource Allocation in Shared Computer Systems,'' DEC Research Report TR-301, 1984.
\bibitem{kelly1996} F. P. Kelly, ``Notes on Effective Bandwidths,'' in \textit{Stochastic Networks: Theory and Applications}, Oxford University Press, 1996, pp. 141--168.
\bibitem{shwartz1995} A. Shwartz and A. Weiss, \textit{Large Deviations for Performance Analysis}, Chapman and Hall, 1995.
\bibitem{itu-p838} International Telecommunication Union, ``Specific Attenuation Model for Rain for Use in Prediction Methods,'' \textit{Recommendation ITU-R P.838-3}, 2005.
\bibitem{itu-p618} International Telecommunication Union, ``Propagation Data and Prediction Methods Required for the Design of Earth-Space Telecommunication Systems,'' \textit{Recommendation ITU-R P.618}, 2017.
\bibitem{mohan2023starlink} N. Mohan \textit{et al.}, ``A Multifaceted Look at Starlink Performance,'' \textit{arXiv:2310.09242}, 2023.
\bibitem{ullah2025starlink} M. A. Ullah \textit{et al.}, ``A First Look at Starlink In-Flight Performance: An Intercontinental Empirical Study,'' \textit{arXiv:2508.09839}, 2025.
\bibitem{wu2024handover} J. Wu \textit{et al.}, ``Accelerating Handover in Mobile Satellite Network,'' \textit{arXiv:2403.11502}, 2024.
\bibitem{worldbank-digitalnepal2022} World Bank, \textit{Digital Nepal Acceleration Project}, Project Appraisal Document, 2022.
\bibitem{nta-mis2024} Nepal Telecommunications Authority, \textit{Management Information System Reports and Telecommunications Indicators}, Regulatory Statistical Reports, 2024.
\bibitem{hevner2004design} A. R. Hevner \textit{et al.}, ``Design Science in Information Systems Research,'' \textit{MIS Quarterly}, vol. 28, no. 1, pp. 75--105, 2004.

\end{thebibliography}
